Selective Sequential Model Selection

### 2015-11-10 paper.tex
discussion of which penalties we handle

>>>>

\JTcomment{I agree that it is worth distinguishing ``provable''
and ``computable''.
I agree that the collection of things we can prove things about
includes group LASSO perhaps other many penalties, but
I would say
that we only have a practical algorithm for computing
when the penalty is $\ell_1$ in this paper. I'm not sure exactly
how to fit nuclear norm here because I'm not sure what
we should call the  ever active set when the loss is not Frobenius (i.e. unless
we are doing PCA or SVT). That is, in matrix
completion or reduced-rank regression I'm not sure what I would call the 
ever-active set. For PCA or SVT, the spaces produced by the data's left and
right singular vectors make up (a reasonable version of an) ever-active set.

I also understand your argument that for $\ell_1$  the next entry test is less bad than I thought. 
To check the KKT conditions at $\hat{\theta}^{\lambda}(Y)$ for $\ell_1$ is 
straightforward, as $\hat{\theta}^{\lambda}(Y^*)$ has 
an explicit candidate form so we have a very good guess
at what the residuals at slightly later $\lambda$'s should look like and we
can check the KKT conditions easily.
For group LASSO, things are more complicated
as we probably will not want to condition on the ``signs'' which are now
a collection of unit vectors. If we don't condition on them
then we have to solve group LASSO for response $Y^*$ until the set of
active groups changes.
Even if we do condition on them (which is OK
as they are measurable with respect the right $\sigma$-algebra) the simplification for sampling that we observe for $\ell_1$ goes away. After $k$ steps on the
discrete $\Lambda$ path I think we are back to having 
$O(p*k)$ constraints roughly for any penalty that is not $\ell_1$. (For group
LASSO, the $O(p*k)$ estimate assumes $k$ is not huge, and each group has roughly bounded number of features in it.)}
